---
title: "P8105_HW#6_qx2199"
date: "12/08/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)
```

```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("./homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2



```{r}
baby_df = read_csv("./birthweight.csv") %>% 
 janitor::clean_names() %>% 
  mutate(
    babysex = case_when(
      babysex == "1" ~ "male",
      babysex == "2" ~ "female",
      TRUE ~ as.character(babysex)
    ),
    frace = case_when(
      frace == "1" ~ "white",
      frace == "2" ~ "black",
      frace == "3" ~ "Asian",
      frace == "4" ~ "Puerto Rican",
      frace == "8" ~ "Other",
      frace == "9" ~ "Unknown",
      TRUE ~ as.character(frace)
    ),
     mrace = case_when(
      mrace == "1" ~ "white",
      mrace == "2" ~ "black",
      mrace == "3" ~ "Asian",
      mrace == "4" ~ "Puerto Rican",
      mrace == "8" ~ "Other",
      mrace == "9" ~ "Unknown",
      TRUE ~ as.character(mrace)
      ),
    malform = case_when(
      malform == "0" ~ "absent",
      malform == "1" ~ "present",
      TRUE ~ as.character(malform)
       ))

baby_df %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    mrace = as.factor(mrace),
    malform = as.factor(malform)
    
  )
baby_df %>% 
  anyNA()

```

The birthweight data contains `r baby_df %>% nrow()` rows, `r baby_df %>% ncol()` columns, and no missing data. 

###fit a model

fitting a model by using backward method. We want to find out he predictors that we want to put in our model. 

```{r}
model_crude = lm(bwt  ~ ., data = baby_df)
step(model_crude, direction='backward') 

summary(model_crude)
```

From the output, we could see that the variables that we want to include in our model are: `babysex`  `bhead`  `blength` `delwt` `fincome`  `gaweeks` `mheight` `mrace` `parity` `ppwt` ` smoken`  

####fit the model with these variables:
```{r}
model_fit = lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = baby_df) 
```


```{r}
  baby_df %>% 
  add_residuals(model_fit) %>% 
  add_predictions(model_fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) + labs( title = "Residuals against Fitted Values", x = "Fitted Value", y = "Residuals")
```
From the residual plot, we could see that most of the residuals are not heavily skewed,especially when the predicted value is higher than 2000g.  However, when the predicted values are smaller than 2000, there are outliers; when the predicted value decrease, residual goes up.


*Compare your model to two others:
One using length at birth and gestational age as predictors (main effects only)
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

```{r}
cross_validation = 
  crossv_mc(baby_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) %>% 
  mutate(
    model_one = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_main = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_inter = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x))) %>% 
  mutate(
    rmse_one = map2_dbl(model_one, test, ~rmse(model = .x, data = .y)),
    rmse_main = map2_dbl(model_main, test, ~rmse(model = .x, data = .y)),
    rmse_inter = map2_dbl(model_inter, test, ~rmse(model = .x, data = .y)),
  )

rmse_plot = 
  cross_validation  %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) +
  geom_violin(alpha = 0.5) +
  labs( title = "Cross Validation Comparisons", x = "Model", y = "RMSE")
   
rmse_plot

```

According to the average RMSE value and the violin plot,  my model (with preictors: `babysex`  `bhead`  `blength` `delwt` `fincome`  `gaweeks` `mheight` `mrace` `parity` `ppwt` ` smoken` ) has the lowest RMSE. Therefore, it's the best model among the three.The model with only main effects ( `blength` `gaweeks` ) has the highest RMSE and hence is the worst one.The model with  length, sex, and all interactions has the medium RMSE among the three models. Therefore, it's the second best model. 



#problem 3

load the data 
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

*Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

```{r}
weather_new = 
weather_df %>% 
modelr::bootstrap(n = 5000) %>% 
mutate(
  models = map(.x = strap, ~ lm(tmax ~ tmin, data = .x)),
  r_glance = map(models, broom::glance),
  beta = map(models, broom::tidy),
  )

weather_final=
  weather_new %>%  
  unnest(r_glance,beta) %>%  
  select(.id, term, estimate, r.squared) %>% 
  pivot_wider( names_from = term,values_from = estimate) %>% 
  janitor::clean_names() %>% 
  mutate(log_one_zero = log(intercept*tmin))

```


```{r}
 weather_final %>% 
  ggplot(aes(x = r_squared)) + 
  geom_density()
```

For the r squared distribution plot, it's little-bit left-skewed with the mean of `r mean( weather_final$r_squared)`
```{r}
 weather_final %>% 
  ggplot(aes(x = log_one_zero)) + 
  geom_density()
```
The log(beta0 *beta1) plot,it's approximately normal-distributed, with the mean of `r mean( weather_final$log_one_zero)`

```{r}
r_ci = 
  weather_final %>% 
  summarize(
   r_ci_lower = quantile(r_squared, 0.025),
   r_ci_upper = quantile(r_squared, 0.975)
  ) %>% 
  knitr::kable(digits = 3)
r_ci
```

95%CI for r-square is (0.894, 0.927)

```{r}
log_ci = 
  weather_final %>% 
  summarize(
   log_ci_lower = quantile(log_one_zero, 0.025),
   log_ci_upper = quantile(log_one_zero, 0.975)
  ) %>% 
  knitr::kable(digits =3)
log_ci
```
95%CI  for log(beta0 * beta1) is (1.967, 2.059)



